Artin Group Presentations Arising from Cluster Algebras

### 2014-08-18 Paper.tex
Section 5 Edits

\title{Artin Group Presentations Arising from Cluster Algebras}
\author{Jacob Haley, David Hemminger, Aaron Landesman, Hailee Peck}
\address{Jacob: 225 St. Edward's Hall; Notre Dame, IN 46556 \\
Hailee: 1184 W Main St; Decatur, IL 62522}
\email{jhaley3@nd.edu, david.hemminger@duke.edu, aaronlandesman@college.harvard.com, hpeck@millikin.edu}
\date{\today}
\keywords{Artin group, cluster algebra, diagram representations}

@@

\section{Symmetry among (R3) Relations}
\label{sec:one_relation}

@@

\begin{lem}
Let $\Gamma$ be a diagram of finite type which contains a chordless cycle C:

@@

so that all edges have weight 1. Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (T2) and $t(i_{a}, i_{a+1})$ for some a $\in \{1, \dots, d\}$, all of the relations in (T3) hold for C.
\end{lem}

\begin{proof}
It suffices to prove that the relation t(0, 1) implies the relation t(d-1, 0), as the other relations will follow by induction. So suppose $A_{\Gamma}$ satisfies the relation t(0, 1). Then we have
\begin{align*}
s_{d-1}p_{d-1, 0} & = s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
&= s_{0}^{-1}s_{0}s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} &\text{by (T2)} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{1})s_{d-1}s_{0} &\text{by (T2)}\\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{0})s_{d-1}s_{0} &\text{by t(0, 1)}\\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{0})s_{d-1}s_{0} &\text{by (T2)}\\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}s_{0}^{-1}s_{0} &\text{by (T2)}\\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} = p_{d-1, 0}s_{d-1}
\end{align*}
as required. Note that line 3 is equal to 4 and line 7 is equal to line 8 since the cycle is chordless, meaning that $s_{d-1}$ commutes with every element except $s_{0}$ and $s_{d-2}$.
\end{proof}
Furthermore, we obtain similar results for cycles containing edges of weight 2.
\begin{lem} \label{2tri}
Let $\Gamma$ be a diagram of finite type containing the following 3-cycle:

@@

   \end{tikzpicture}
and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations t(i, j) and t(k, i) are equivalent.
\end{lem}

\begin{proof}
The lemma follows from the fact that
\begin{align*}
& s_{k}^{-1}s_{j}(s_{i}p_{i, j}s_{i}^{-1}p_{i, j}^{-1})s_{j}^{-1}s_{k} \\
& s_{k}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{j})s_{j}^{-1}s_{k} \\
&= s_{k}^{-1}s_{j}s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1} \\
&= s_{k}^{-1}s_{i}^{-1}s_{j}s_{i}s_{k}s_{i}^{-1}s_{j}^{-1}s_{i} \\
&= s_{k}^{-1}p_{k, i}s_{k}p_{k, i}^{-1}
\end{align*}
\end{proof}

@@

\begin{lem}\label{lem:extra_square_relation}
Suppose $\Gamma$ contains a 3-cycle with edges of weight 2, labeled as in ~\ref{2tri}, and suppose that A$_{\Gamma}$ is generated by $s_{1}, \dots s_{n}$. Then we have that
$$s_{j}p_{j, k}s_{j}p_{j, k}^{-1}s_{j}^{-1}p_{j, k}^{-1} := s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}^{-1}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$
\end{lem}

\begin{proof}
We first show that
$$s_{j}^{-1}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$
The result then follows by inverting the relation and conjugating by $s_{j}$. In the following computation, we will underline the terms being manipulated in each line for emphasis.

@@

\begin{lem} \label{2sqr}
Let $\Gamma$ be a diagram of finite type containing the following 4-cycle:
\begin{tikzpicture}[baseline=-0.5ex]
\matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
  {
    & |[name = ul]|{i}\circ& |[name = ur]|\circ{j}\\
    %
    &|[name=dl]|{l} \circ &|[name=dr]| \circ{k} \\
  };
\draw[->]
  (ul) to node[above] {1} (ur)
  ;
  \draw[->]
  (dl) to node[left]{2}(ul)
  ;
  \draw[->]
  (dr) to node[below]{1}(dl)
  ;
  \draw[->]
  (ur) to node[right]{2} (dr)
  ;
\end{tikzpicture}
and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations t(i, j) and t(k, l) are equivalent.
\end{lem}

\begin{proof}
We have that
\begin{align*}
& s_{k}^{-1}s_{l}^{-1}s_{j}(s_{i}p_{i, j}s_{i}^{-1}p_{i, j}^{-1})s_{j}^{-1}s_{l}s_{k} \\
&= s_{k}^{-1}s_{l}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{l}^{-1}s_{k}s_{j})s_{j}^{-1}s_{l}s_{k} \\
&= s_{k}^{-1}s_{l}^{-1}(s_{j}s_{i}s_{j}^{-1})(s_{k}^{-1}s_{l}s_{k})(s_{j}s_{i}^{-1}s_{j}^{-1})s_{k}^{-1}s_{l}^{-1}s_{k}s_{l}s_{k} \\
&= s_{k}^{-1}s_{l}^{-1}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i}s_{k}^{-1}(s_{l}^{-1}s_{k}s_{l})s_{k} \\
&= s_{k}^{-1}s_{l}^{-1}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i}s_{l} \\
&= s_{k}^{-1}p_{k, l}s_{k}p_{k, l}^{-1}
\end{align*}
\end{proof}

@@

\begin{lem}\label{lem:op_homomorphism}
Let A$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$, and let A$_{\Gamma^{op}}$ be generated by $r_{1}, \dots, r_{n}$. Then the map $$\Delta: s_{i} \rightarrow r_{i}^{-1}$$ defines an isomorphism between A$_{\Gamma}$ and A$_{\Gamma^{op}}.$
\end{lem}
\begin{proof}
It suffices to show that the map is well-defined, or that the elements $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (T2) and (T3) of A$_{\Gamma^{op}}$. One can see that the inverse elements satisfy (T2) in A$_{\Gamma^{op}}$ by taking the inverse of both sides of the corresponding relation in A$_{\Gamma}$. To see that the elements satisfy (T3) in A$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation t(0,1) in (T3) in A$_{\Gamma}$. But then applying relations from (T2), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle is chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this occurs if and only if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation t(0, d-1) in A$_{\Gamma^{op}}.$

For a triangle labeled as in ~\ref{2tri}, by the relation t(k, i) we have $$s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1} = s_{i}^{-1}s_{j}s_{i}.$$ Hence $$s_{k}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1} = s_{j}s_{i}s_{j}^{-1}.$$ But as before, this can occur if and only if $s_{i}^{-1}, s_{j}^{-1}, s_{k}^{-1}$ satisfy the relation t(k, j) in A$_{\Gamma^{op}}$.

Finally, given a square labeled as in ~\ref{2sqr} and the relations t(1, 2) and t(3, 4), we have
\begin{align*}
& s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1} \\
&= s_{i}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1} \\
&= s_{i}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{i}^{-1} \\
&= s_{i}s_{j}(s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{j})s_{j}^{-1}s_{i}^{-1} \\
&= s_{i}s_{j}s_{j}^{-1}(s_{k}^{-1}s_{l}s_{k})s_{j}(s_{i}s_{j}^{-1}s_{i}^{-1}) \\
&= s_{i}s_{l}s_{k}s_{l}^{-1}s_{j}s_{j}^{-1}s_{i}^{-1}s_{j} \\
&= s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}
\end{align*}
But this relation holds if and only if $s_{i}^{-1}, \dots, s_{l}^{-1}$ satisfy t(j, i) in A$_{\Gamma^{op}}$. Therefore, we are done.
\end{proof}

>>>>

\title{Artin Group Presentations Arising from Cluster Algebras}
\author{Jacob Haley, David Hemminger, Aaron Landesman, Hailee Peck}
\address{Jacob: University of Notre Dame \\
Hailee: 1184 W Main St; Decatur, IL 62522}
\email{jhaley3@nd.edu, david.hemminger@duke.edu, aaronlandesman@college.harvard.com, hpeck@millikin.edu}
\date{\today}
\keywords{Artin group, cluster algebra, diagram representations}

@@

\section{Symmetry among the (R3) Relations}
\label{sec:one_relation}

@@

\begin{lem} \label{Sym-Lem}
Let $\Gamma$ be a diagram of finite type which contains a chordless cycle C:

@@

so that all edges have weight 1. Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (T2) and $t(i_{a}, i_{a+1}) = e$ for some a $\in \{1, \dots, d\}$, all of the relations in (T3) hold for C.
\end{lem}

In the proof of this Lemma and throughout the rest of the paper, we will frequently employ the following relations, which follow from the (T2) relations.

\begin{lem} \label{Extra-Rel}
Let $\Gamma$ be a diagram of finite type, and let $A_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then we have that 
\begin{enumerate}[(a)]
\item $s_{i}s_{j}s_{i}^{-1} = s_{j}^{-1}s_{i}s_{j}$ if there is an arrow of weight 1 from i to j in $\Gamma$ \\
\item $s_{i}s_{j}s_{i}^{-1}s_{j}^{-1} = s_{j}^{-1}s_{i}^{-1}s_{j}s_{i}$ if there is an arrow of weight 2 from i to j in $\Gamma$
\end{enumerate}
\end{lem}

\begin{proof}[Proof of \ref{Extra-Rel}]
The relation in (a) follows immediately from the (T2) relation $s_{j}s_{i}s_{j} = s_{i}s_{j}s_{i}$ by left multiplying both sides by $s_{j}^{-1}$ and right multiplying both sides by $s_{i}^{-1}$. Similarly, the relation in (b) arises from the (T2) relation $s_{j}s_{i}s_{j}s_{i} = s_{i}s_{j}s_{i}s_{j}$ by left multiplying both sides by $s_{i}^{-1}s_{j}^{-1}$ and right multiplying both sides by $s_{j}^{-1}s_{i}^{-1}$
\end{proof}   
\begin{proof}[Proof of \ref{Sym-Lem}]
It suffices to prove that the relation t(0, 1) = e implies that t(d-1, 0) = e, as the other relations will follow by induction. So suppose $A_{\Gamma}$ satisfies the relation t(0, 1) = e. Then we have
\begin{align*}
s_{d-1}p(d-1, 0) & = s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
&= s_{0}^{-1}s_{0}s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} &\text{by (T2)} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{1})s_{d-1}s_{0} &\text{by (T2)}\\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{0})s_{d-1}s_{0} &\text{by t(0, 1) = e}\\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{0})s_{d-1}s_{0} &\text{by (T2)}\\
&= s_{0}^{-1}(s_{d-1}^{-1}s_{d-1})s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}s_{0}^{-1}s_{0} &\text{by (T2)}\\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} = p(d-1, 0)s_{d-1}
\end{align*}
as required. Note that line 3 is equal to 4 and line 7 is equal to line 8 since the cycle is chordless, meaning that $s_{d-1}$ commutes with every element except $s_{0}$ and $s_{d-2}$.
\end{proof}
Furthermore, we obtain similar results for cycles containing edges of weight 2.
\begin{lem} \label{2tri}
Let $\Gamma$ be a diagram of finite type containing the following 3-cycle:

@@

   \end{tikzpicture}
and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations t(i, j) = e and t(k, i) = e are equivalent.
\end{lem}

\begin{proof}
The lemma follows from the fact that
\begin{align*}
& s_{k}^{-1}s_{j}(s_{i}p(i, j)s_{i}^{-1}p(i, j)^{-1})s_{j}^{-1}s_{k} \\
&= s_{k}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{j})s_{j}^{-1}s_{k} \\
&= s_{k}^{-1}s_{j}s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1} \\
&= s_{k}^{-1}s_{i}^{-1}s_{j}s_{i}s_{k}s_{i}^{-1}s_{j}^{-1}s_{i} \\
&= s_{k}^{-1}p(k, i)s_{k}p(k, i)^{-1}
\end{align*}
\end{proof}

@@

\begin{lem}\label{lem:extra_square_relation}
Suppose $\Gamma$ contains a 3-cycle with edges of weight 2, labeled as in ~\ref{2tri}, and suppose that A$_{\Gamma}$ is generated by $s_{1}, \dots s_{n}$. Then we have that
$$s_{j}p(j, k)s_{j}p(j, k)^{-1}s_{j}^{-1}p(j, k)^{-1} := s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}^{-1}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$
\end{lem}

\begin{proof}
We show that
$$s_{j}^{-1}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$
The result then follows by inverting the relation and conjugating by $s_{j}$. In the following computation, we will underline the terms being manipulated in each line for emphasis.

@@

\begin{lem} \label{2sqr}
Let $\Gamma$ be a diagram of finite type containing the following 4-cycle:
\begin{tikzpicture}[baseline=-0.5ex]
\matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
  {
    & |[name = ul]|{i}\circ& |[name = ur]|\circ{j}\\
    %
    &|[name=dl]|{l} \circ &|[name=dr]| \circ{k} \\
  };
\draw[->]
  (ul) to node[above] {1} (ur)
  ;
  \draw[->]
  (dl) to node[left]{2}(ul)
  ;
  \draw[->]
  (dr) to node[below]{1}(dl)
  ;
  \draw[->]
  (ur) to node[right]{2} (dr)
  ;
\end{tikzpicture}
and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations t(i, j) = e and t(k, l) = e are equivalent.
\end{lem}

\begin{proof}
We have that
\begin{align*}
& s_{k}^{-1}s_{l}^{-1}s_{j}(s_{i}p(i, j)s_{i}^{-1}p(i, j)^{-1})s_{j}^{-1}s_{l}s_{k} \\
&= s_{k}^{-1}s_{l}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{l}^{-1}s_{k}s_{j})s_{j}^{-1}s_{l}s_{k} \\
&= s_{k}^{-1}s_{l}^{-1}(s_{j}s_{i}s_{j}^{-1})(s_{k}^{-1}s_{l}s_{k})(s_{j}s_{i}^{-1}s_{j}^{-1})s_{k}^{-1}s_{l}^{-1}s_{k}s_{l}s_{k} \\
&= s_{k}^{-1}s_{l}^{-1}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i}s_{k}^{-1}(s_{l}^{-1}s_{k}s_{l})s_{k} \\
&= s_{k}^{-1}s_{l}^{-1}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i}s_{l} \\
&= s_{k}^{-1}p(k, l)s_{k}p(k, l)^{-1}
\end{align*}
\end{proof}

@@

\begin{lem}\label{lem:op_homomorphism}
Let A$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$, and let A$_{\Gamma^{op}}$ be generated by $r_{1}, \dots, r_{n}$. Then the map $$\Delta: s_{i} \rightarrow r_{i}^{-1}$$ defines an isomorphism between A$_{\Gamma}$ and A$_{\Gamma^{op}}.$
\end{lem}
\begin{proof}
It suffices to show that the map is well-defined, or that the elements $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (T2) and (T3) of A$_{\Gamma^{op}}$. One can see that the inverse elements satisfy (T2) in A$_{\Gamma^{op}}$ by taking the inverse of both sides of the corresponding relation in A$_{\Gamma}$. To see that the elements satisfy (T3) in A$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}s_{0}$$ by the relation t(0,1) = e in (T3) in A$_{\Gamma}$. But then applying relations from (T2), we have that $$s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{1} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1}s_{0},$$ and since the cycle is chordless, we then have $$s_{0}s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}.$$ Repeating this process, we find that $$s_{0}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0}.$$ But this occurs if and only if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation t(0, d-1) = e in A$_{\Gamma^{op}}.$

For a triangle labeled as in ~\ref{2tri}, by the relation t(k, i) = e we have $$s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1} = s_{i}^{-1}s_{j}s_{i}.$$ Hence $$s_{k}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1} = s_{j}s_{i}s_{j}^{-1}.$$ But as before, this can occur if and only if $s_{i}^{-1}, s_{j}^{-1}, s_{k}^{-1}$ satisfy the relation t(k, j) = e in A$_{\Gamma^{op}}$.

Finally, given a square labeled as in ~\ref{2sqr} and the relations t(1, 2) = e and t(3, 4) = e, we have
\begin{align*}
& s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1} \\
&= s_{i}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1} \\
&= s_{i}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{i}^{-1} \\
&= s_{i}s_{j}(s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{j})s_{j}^{-1}s_{i}^{-1} \\
&= s_{i}s_{j}s_{j}^{-1}(s_{k}^{-1}s_{l}s_{k})s_{j}(s_{i}s_{j}^{-1}s_{i}^{-1}) \\
&= s_{i}s_{l}s_{k}s_{l}^{-1}s_{j}s_{j}^{-1}s_{i}^{-1}s_{j} \\
&= s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}
\end{align*}
But this relation holds if and only if $s_{i}^{-1}, \dots, s_{l}^{-1}$ satisfy t(j, i) = e in A$_{\Gamma^{op}}$. Therefore, we are done.
\end{proof}
